\chapter{Ariel Castro}

\caseheader{001}{Pre-reveal profile}

\begin{center}
  \fcolorbox{rulegray}{softgray}{%
    \begin{minipage}[c][0.26\textheight][c]{0.42\linewidth}
      \centering
      \large Portrait pending

      \small Rights-cleared pre-arrest image needed.
    \end{minipage}
  }
\end{center}

\vspace{0.2em}

\begin{tabularx}{\linewidth}{>{\bfseries}p{0.28\linewidth}X}
Name & Ariel Castro\\
Birth & Puerto Rico, 1960\\
Primary residence & Cleveland, Ohio\\
Public roles & School bus driver; local musician; homeowner\\
Known public pattern & Long-term neighborhood presence, ordinary employment history, family and social connections\\
Community surface & Neighbors described routine social contact, outdoor activity, music, and ordinary errands.\\
Pre-reveal note & The visible profile alone gives no reliable answer about private conduct or concealed risk.\\
\end{tabularx}

\vfill

\begin{center}
  \fcolorbox{rulegray}{softgray}{%
    \begin{minipage}{0.86\linewidth}
      \centering
      \Large\bfseries Reader Decision

      \normalsize
      Based only on this neutral profile, mark your answer before turning the page.

      \vspace{0.8em}
      \checkbox\ Evil
      \hspace{1.2em}
      \checkbox\ Not evil
      \hspace{1.2em}
      \checkbox\ Not enough information
    \end{minipage}
  }
\end{center}

\clearpage

\caseheader{001}{Reveal}

{\Large\bfseries Disposition: known serious criminal offender}

\begin{tabularx}{\linewidth}{>{\bfseries}p{0.28\linewidth}X}
Subject & Ariel Castro\\
Case location & Cleveland, Ohio\\
Criminal conduct & Abduction, captivity, rape, and related offenses involving Michelle Knight, Amanda Berry, and Gina DeJesus\\
Known period & 2002 to May 6, 2013\\
Prosecution & Local prosecution in Cuyahoga County, with FBI investigative and victim-assistance support\\
Sentence & Life imprisonment without possibility of parole, plus 1,000 years\\
Final status & Died in Ohio custody on September 3, 2013\\
\end{tabularx}

\section*{Investigative Summary}

\begin{itemize}
  \item Castro maintained a conventional public identity as a Cleveland resident, former school bus driver, musician, father, and homeowner.
  \item In May 2013, three women who had disappeared in separate years were found alive at his Seymour Avenue residence.
  \item FBI Cleveland states that the women had been held captive for more than a decade and that the investigation received FBI evidence response, behavioral, tactical, and victim-assistance support.
  \item Ohio Bureau of Criminal Investigation DNA testing confirmed Castro as the father of the child born to Amanda Berry during captivity.
  \item The plea agreement included demolition of the Seymour Avenue house. The court sentence ensured Castro would not be released.
\end{itemize}

\section*{Profile Lesson}

The neutral facts were real but incomplete. A public routine, stable address,
ordinary employment, and recognizable community role did not disclose the
conduct later established in court. The puzzle answer is therefore not based on
appearance. It is based on documented conduct.

\clearpage

\section*{Source Notes}

\begin{itemize}
  \item Neutral biographical details: CBS News, ``Who is Cleveland kidnapping suspect Ariel Castro?'' May 9, 2013. \url{https://www.cbsnews.com/news/who-is-cleveland-kidnapping-suspect-ariel-castro/}
  \item FBI case context and sentence summary: FBI Cleveland field office history. \url{https://www.fbi.gov/history/field-office-histories/cleveland}
  \item DNA result: Ohio Attorney General, ``Attorney General DeWine Announces DNA Results in Cleveland Kidnapping Case,'' May 10, 2013. \url{https://www.ohioattorneygeneral.gov/Media/News-Releases/May-2013/Attorney-General-DeWine-Announces-DNA-Results-in-C}
  \item Custody death and offense summary: Ohio Department of Rehabilitation and Correction consultant report, November 22, 2013. \url{https://mediaassets.news5cleveland.com/uploads/Castro-FINALODRC-SUICIDE-REPORT-2013.pdf}
  \item Court source retained locally: \path{sources/ariel_castro/cuyahoga_sentencing_memorandum.pdf}.
  \item Image status: the 2001 photograph on Wikipedia, \path{File:ArielCastro.jpg}, is marked as non-free/fair-use and was not included in this rights-clean build. \url{https://en.wikipedia.org/wiki/File:ArielCastro.jpg}
\end{itemize}
